\documentclass[a4paper,11pt]{scrartcl}
\usepackage{releasenotes} % Your custom style (fine to reuse)
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{enumitem}
\usepackage{hyperref}

\title{User Manual\\Kaiju Academy}
\author{Group A2}
\date{\today}

\begin{document}

\maketitle

\section*{User Manual}
\addcontentsline{toc}{section}{User Manual}

\tableofcontents
\newpage

\section{Introduction}

Kaiju Academy is a web-based e-learning platform for programming education, supporting interactive code assessments, course management, and user progress tracking. This manual guides students and educators in using the system’s main features.



\section{System requirements}
To ensure smooth and reliable access to Kaiju Academy’s full suite of features, users must meet the following system requirements:
\subsection{Browser}
Kaiju Academy is a web-based platform and does not require any software installation. It supports the latest stable versions of:
\begin{itemize}[leftmargin=*]
    \item Google Chrome (recommended)
    \item Mozilla Firefox
    \item Microsoft Edge
    \item Safari
\end{itemize}

\subsection{Operating system}
\begin{itemize}[leftmargin=*]
    \item Windows 10 or later
    \item Mac OS X 10.15 or later
    \item Linux (Ubuntu 20.04 or later recommended)
\end{itemize}

\subsection{Supported Devices}
\begin{itemize}[leftmargin=*]
    \item Desktop computers
    \item Laptops
    \item Tablets (iOS and Android)
    \item Smartphones (iOS and Android)
\end{itemize}

\subsection{Internet Connection}
\begin{itemize}[leftmargin=*]
    \item Recommended: 10+ Mbps for optimal experience, especially when participating in live sessions or loading larger assignments.
\end{itemize}

\subsection{Additional Requirements}
\begin{itemize}[leftmargin=*]
    \item A modern text rendering engine (for syntax highlighting in code editors)
    \item Speakers/headphones (for video lectures or audio-based content)
    \item Microphone and webcam (if participating in live or proctored assessments)
\end{itemize}

\section{Getting Started}

\subsection{Entering Your Licence Key}
Before you can access course content or features, you must enter your unique licence key. The system will prompt you for a key after your first login.

\begin{enumerate}[leftmargin=*]
    \item When prompted, enter your licence key (format example: AAAA-BBBB-CCCC-DDDD).
    \item Click \textbf{Submit}.
    \item If your key is valid, you will be granted access. If not, please check the key and try again, or contact support.
\end{enumerate}

If you have not received a licence key, or if your key does not work, please contact support at \href{mailto:support@kaijuacademy.example.com}{support@kaijuacademy.example.com}.

\subsection{Accessing the Platform}
\begin{itemize}[leftmargin=*]
    \item Open your web browser (Chrome or Firefox recommended).
    \item Visit: \url{https://kaijuacademy.example.com} (replace with real URL).
\end{itemize}

\subsection{Registration}
\begin{enumerate}[leftmargin=*]
    \item Click \textbf{Sign Up}.
    \item Enter your email, password, and required personal details.
    \item If Multi-Factor Authentication (MFA) is enabled, follow on-screen instructions.
    \item Check your email for a verification link and confirm your account.
\end{enumerate}

\subsection{Login}
\begin{enumerate}[leftmargin=*]
    \item Click \textbf{Login}.
    \item Enter your email and password.
    \item If MFA is enabled, enter your authentication code.
    \item Upon successful login, you will be redirected to your dashboard.
\end{enumerate}

\section{User Roles and Dashboard Overview}

\subsection{Students}
\begin{itemize}[leftmargin=*]
    \item View enrolled courses, progress, recommended courses.
    \item Access interactive coding assignments and submit solutions.
    \item Purchase credits to unlock new courses.
\end{itemize}

\subsection{Educators}
\begin{itemize}[leftmargin=*]
    \item Create, update, or delete courses and modules.
    \item Upload materials (videos, PDFs, problems).
    \item View and grade student submissions.
    \item Track course statistics and student progress.
\end{itemize}

\subsection{Navigating the Dashboard}
\begin{itemize}[leftmargin=*]
    \item Use the navigation bar to access \texttt{Courses}, \texttt{Profile}, \texttt{Credit Purchase}, and \texttt{Support}.
\end{itemize}

\section{Courses}

\subsection{Browsing and Enrolling}
\begin{enumerate}[leftmargin=*]
    \item Click on \textbf{Courses}.
    \item Browse or search for available courses.
    \item To enroll, click \textbf{Enroll} (requires sufficient credits for paid courses).
    \item Confirm enrollment; the course will appear in your dashboard.
\end{enumerate}

\subsection{Course Content}
\begin{itemize}[leftmargin=*]
    \item Courses contain modules with lectures, readings, and assignments.
    \item Completed modules are tracked in your profile.
\end{itemize}

\section{Interactive Code Assessment}

\begin{enumerate}[leftmargin=*]
    \item Open a course and select a coding assignment.
    \item Write or edit your code in the provided editor.
    \item Click \textbf{Run} to execute and see results/output.
    \item Click \textbf{Submit} to grade your solution.
    \item View feedback and results.
\end{enumerate}

\section{Profile and Progress Tracking}

\begin{itemize}[leftmargin=*]
    \item Access your profile to view enrolled and recommended courses.
    \item Track progress (completion percentage, badges, achievements).
    \item Update your personal details or change password.
\end{itemize}

\section{Credits and Payment}

\begin{enumerate}[leftmargin=*]
    \item Go to \textbf{Buy Credits}.
    \item Select a credit package and proceed to payment (handled via secure third-party gateway).
    \item On success, credits are added to your account and can be used for enrolling in paid courses.
\end{enumerate}

\section{Error Handling and Support}

\begin{itemize}[leftmargin=*]
    \item Common error messages (e.g., invalid login, insufficient credits) are displayed on screen.
    \item For technical issues, contact support at \href{mailto:support@kaijuacademy.example.com}{support@kaijuacademy.example.com}.
\end{itemize}

\section{Frequently Asked Questions (FAQ)}

\begin{itemize}[leftmargin=*]
    \item \textbf{Q: I forgot my password. What should I do?}
    \begin{itemize}
        \item Click \textbf{Forgot Password} on the login page and follow instructions.
    \end{itemize}
    \item \textbf{Q: How do I get more credits?}
    \begin{itemize}
        \item Use the \textbf{Buy Credits} page in your dashboard.
    \end{itemize}
    \item \textbf{Q: Who do I contact for billing issues?}
    \begin{itemize}
        \item Email: \href{mailto:support@kaijuacademy.example.com}{support@kaijuacademy.example.com}
    \end{itemize}
\end{itemize}

\section{Contact and Support}

\begin{itemize}[leftmargin=*]
    \item For technical support or feedback, contact: \href{mailto:support@kaijuacademy.example.com}{support@kaijuacademy.example.com}
    \item For course content questions, contact your educator via the course page.
\end{itemize}

\section{Acknowledgments}
This document was prepared with the assistance of AI tools (e.g., ChatGPT 4.1) for drafting and review.

\end{document}